\documentclass[]{deedy-resume-openfont}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Lalith Kumar B R}{ \href{mailto:brlalithkumar@gmail.com}{brlalithkumar@gmail.com} | (091) 9790503845 \\
\urlstyle{same}{H-32, Old ASTC, TNHB, Phase-12, Hosur, Tamilnadu, India} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{VIT University}
\descript{MS Software Engineering(integrated)}
\location{2009 - 2014 | Vellore, Tamilnadu}
\location{Cum. GPA: 9.05 / 10.0}
\sectionsep

\subsection{St Josephs}
\descript{12\textsuperscript{th} Std}
\location{2008 - 2009 | Hosur, Tamilnadu}
\location{Aggregate: 94.5\%}
\sectionsep

\subsection{St Josephs}
\descript{10\textsuperscript{th} Std}
\location{2006 - 2007 | Hosur, Tamilnadu}
\location{Aggregate: 93.2\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/lalith26}{\custombold{lalith}} \\
LinkedIn://  \href{https://www.linkedin.com/in/brlalithkumar/}{\custombold{lalith}} \\
Freelancer:// \href{http://www.freelancer.in/u/brlalithkumar.html}{\custombold{lalith}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
Javascript \textbullet{} Java \textbullet{} NodeJS\\ 
 \textbullet{} HTML \textbullet{} CSS\\ 
\location{Moderate:}
C \textbullet{} C++ \textbullet{} Android\\
\location{Familiar:}
MySQL\textbullet{} Photoshop\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{}
A Professional with interest in full stack application development. I work with full stack JavaScript and Java to
build awesome experiences and scalable backend services to supplement it.
\section{Experience}

\runsubsection{PayPal}
\descript{| Software Engineer }
\location{July 2014 - Present | Bengaluru, India}
\vspace{\topsep}
\custombold{MoneyBoxes} Is a replica of a Piggybank. It enables PayPal customers to manage their income by splitting their Income into Buckets. Rules can be setup which get triggered based on various events.  Lead the frontend development team and contributed to a few parts on the backend architecture. The entire tech stack involves the frontend, 2 backend rest services, 1 batch and 2 daemons.\begin{tightemize}
\vspace{\topsep}
\item Currently in beta mode with employee testing underway.
\item Technology used - ReactJS, NodeJS, Kraken, jQuery, Java
\end{tightemize}
\vspace{\topsep}

\custombold{Choicefiserv: A Rest Service} In PayPal, Various types of checkout exists. In general traditional checkout, plans are created upfront. A plan is a combination of instruments which can together fund the cart items. In mobile checkout, a list of Financial Instruments is presented to user and then the plan is created based on user selection to keep the experience slick and fast. \begin{tightemize}
\item Technology used - Java
\end{tightemize}
\vspace{\topsep}

\custombold{Rewards Platform} In PayPal, Customers are rewarded based on various actions. Ex: If a customer does a 100\$ transaction, the customer is eligible for a 2\% cashback.  We manage the entire lifecycle involved in managing rewards to a customer. The entire tech stack involves a backend rest sevice, 1 batch and 1 daemon.\begin{tightemize}
\item Technology used - Java
\end{tightemize}
\vspace{\topsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Other Projects} 
\begin{tightemize}\vspace{\topsep}
\item Have worked on freelancer.com during my pre-final and final year and gained a lot of experience by working on various projects
\item Out of enthusiasm of Learning, Have developed and published a windows phone app called Vocabulary Improver in windows store during my second year in College.
\item Have published a game called Sineball on Android Market which was developed in C++ using cocos2d framework.
\item Have created a watchface for Pebble digital watch using Pebble C SDK and published it to the pebble app store.
\item Have created a few websites and also worked on Node.js and a few front end frameworks like React, Backbone and published a few node modules.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS & AFFILIATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Participations \& Accomplishments} 
\begin{tightemize}\vspace{\topsep}
\item Served as the Committee Coordinator for Web Design during Riviera, the Cultural Fest of VIT in 2012
\item Winner of spot award for top notch performance and rapid delivery while using new internal technologies in PayPal
\item Was awarded Merit Scholarship for academic performance during 2009, 2010, 2011
\item Have been given a rating of 2045 by World Chess Federation\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
